\chapter{Passwords \\
\small{\textit{-- Tamara Gonzalez Ibarra}}}
\index{Passwords} 
\index{Chapter!Passwords}
\label{Chapter::Passwords}

In this chapter, the password rules used for various users and servers in the project are displayed. 
The table below summarizes the rules for username, server, and password, along with hints to remember them. Actual passwords are not included for security reasons.

\section{Password Rules Table}

\begin{longtable}{|l|l|p{4cm}|p{4cm}|}
\hline
\textbf{User} & \textbf{Server} & \textbf{Password Rule} & \textbf{Hint} \\
\hline
\endfirsthead
\multicolumn{4}{c}%
{\tablename\ \thetable\ -- continued from previous page} \\
\hline
\textbf{User} & \textbf{Server} & \textbf{Password Rule} & \textbf{Hint} \\
\hline
\endhead
\hline \multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot

Name1 & Server A & At least 8 characters, includes uppercase, lowercase, and a number & Think of your favorite animal and a memorable year. \\
\hline
Name2 & Server B & Minimum 10 characters, includes special character & Combine your favorite color and the number of letters in your hometown. \\
\hline
Tamy & Server C & Must include at least 1 uppercase letter, 1 lowercase letter, and 1 number; 10 characters & At least 12 characters, no repeating characters. Use the first letters of a favorite quote. \\
\hline
\textbf{Bugzilla Admin} & \textbf{167.99.121.94 (Bugzilla Docker)} & At least 10 characters; include site-specific suffix (e.g., \texttt{@bugzilla}); combine shared key with service name & Use format \texttt{<key>@bugzilla} — shared key + service name. \\
\hline
\textbf{Overleaf Admin} & \textbf{167.99.121.94 (Overleaf Docker)} & At least 10 characters; include site-specific suffix (e.g., \texttt{@overleaf}); combine shared key with service name & Use format \texttt{<key>@overleaf} — shared key + service name. \\
\hline
\textbf{Database User} & \textbf{Local Docker DBs} & At least 10 characters; include mix of upper/lowercase and a dot to indicate database scope & Use format \texttt{key.db} — same key used across both DBs with unique suffix. \\
\hline
\end{longtable}

\section{Notes on Password Rules}

All passwords are designed to be strong but memorable using personal hints. Users should avoid writing down passwords directly and instead rely on hints or a secure password manager.
