\chapter{Project Proposal \\
\small{\textit{-- Tamara Gonzalez Ibarra, Michelle Elias Flores, Sydney Winstead}}}
\index{Project Proposal} 
\index{Chapter!itProjectProposal}
\label{Chapter::itProjectProposal}

\section{Project Description}

Our group project for DevOps Principles and Practices is a web-based endless runner game called \textbf{Everscape}. The player controls a character that runs infinitely through a side-scrolling environment, avoiding increasingly challenging obstacles and collecting doubloons for bonus points. Users will compete for high scores, which will be securely stored in a backend database. Application security (e.g., preventing score tampering) and pipeline security (e.g., scanning Docker images) are a focus.

The project aims not only to deliver an engaging and aesthetically pleasing gaming experience but also to integrate DevSecOps practices throughout the development lifecycle.

\section{Sample Tasks}

\subsection*{Game Development}
\begin{itemize}
    \item Build the endless runner game logic, including jumping, collision detection, and scoring.
    \item Create a frontend interface for the player.
    \item Develop a backend service for storing scores.
\end{itemize}

\subsection*{DevSecOps Integration}
\begin{itemize}
    \item \textbf{Source Control}: Use GitHub for version control, pull requests, and branching.
    \item \textbf{Containerization}: Docker to containerize the frontend, backend, and database services.
    \item \textbf{Databases}: Deploy a lightweight containerized database (e.g., MySQL) for scores.
    \item \textbf{Testing}: Write unit tests (e.g., collision detection, score validation) and integration tests (e.g., API endpoints).
    \item \textbf{CI/CD Pipeline}: Set up GitHub Actions to build, test, and deploy containers automatically.
    \item \textbf{Hosting}: Deploy to a containerized environment (AWS ECS or Docker Compose locally).
\end{itemize}
